Generalized spaces for constructive algebra

### 2020-06-21 announcement-agda-workshop.tex
Slides for the first session of the Agda workshop in Padova

  \begin{columns}
    \begin{column}{0.47\textwidth}
      Agda is \ldots
      \begin{enumerate}
        \item a programming language
        \item a \hil{proof language}
        \item<3-> somewhat hard to learn on one's own
        \item<3-> \hil{fun and easy} to learn as part of a course
      \end{enumerate}
    \end{column}

    \begin{column}[t]{0.61\textwidth}
      \only<1>{\includegraphics[width=1.0\textwidth,align=t]{agda-example}}
      \only<2->{
        With Agda you can \ldots
        \begin{enumerate}
          \item ensure \hil{correctness} of proofs
          \item \mbox{\hil{practically explore} type theory}
          \item appreciate mathematics from a new point of view
        \end{enumerate}

        \bigskip
        \centering\hil{``proving $=$ programming''}
      }
    \end{column}
  \end{columns}
\end{frame}

>>>>

  \begin{columns}
    \begin{column}{0.47\textwidth}
      Agda is \ldots
      \begin{enumerate}
        \item a programming language
        \item a \hil{proof language}
        \item<4-> somewhat hard to learn on one's own
        \item<4-> \hil{fun and easy} to learn as part of a course
      \end{enumerate}
    \end{column}

    \begin{column}[t]{0.61\textwidth}
      \only<1>{\includegraphics[width=1.0\textwidth,align=t]{agda-example}}
      \only<2->{
        With Agda you can \ldots
        \begin{enumerate}
          \item ensure \hil{correctness} of proofs
          \item \mbox{\hil{practically explore} type theory}
          \item appreciate mathematics \hil{from a new point of view}
          \item \hil{verify correctness} of programs
        \end{enumerate}
      }
    \end{column}
  \end{columns}

  \pause\pause
  \vspace*{-22em}\hspace*{-1.5em}\small
  \vbox{
    \textit{Three mottos}: \\[-0.6em]
    \begin{enumerate}\scriptsize
      \item ``proving $=$ programming'' \\[-1.2em]
      \item ``conjecturing $=$ specifying'' \\[-1.2em]
      \item ``induction $=$ recursion''
    \end{enumerate}
  }
\end{frame}

\newcommand{\imgslide}[1]{{\usebackgroundtemplate{\parbox[c][\paperheight][c]{\paperwidth}{\centering\includegraphics[height=\paperheight]{#1}}}\begin{frame}[plain]\end{frame}}}

\imgslide{announcement-agda-workshop/catarina-coquand}
\imgslide{announcement-agda-workshop/martin-escardo}
\imgslide{announcement-agda-workshop/pc2018}
\imgslide{announcement-agda-workshop/fischbachau}

\begin{frame}[plain]
  \centering
  \medskip

  \includegraphics[width=0.8\textwidth]{agda-course/wendelstein-1}

  \includegraphics[height=0.245\textwidth]{agda-course/wendelstein-2}
  \includegraphics[height=0.245\textwidth]{agda-course/wendelstein-3}
\end{frame}

\imgslide{agda-course/agda-wiki}
